Mission-time LTL (MLTL) Formula Validation Via Regular Expressions\thanks{Work supported in part by [omitted for blind review] {\bf Note that all references to appendices will be replaced with URLs in the final paper; they are appendices only for blind review.}}

### 2022-10-11 paper/Paper.tex
squished example of regex simp theorem
initial draft of WEST algorithm in section 4

%KYR: need to ensure included packages don't interfere with LNCS style
%\usepackage[utf8]{inputenc}
%\usepackage{amsthm, amsmath, amssymb}
\usepackage{amsfonts} %mathbb
\usepackage{amsmath} %hdots
\usepackage{amssymb} %blacksquare
\usepackage{mathabx} %vDash
\usepackage{mathrsfs} %mathscr
\usepackage{blkarray} %for blockarray
%\usepackage{textcomp}
%\usepackage{xcolor}
%\usepackage{soul}
%\usepackage{ dsfont }
\usepackage{hyperref}
\usepackage{cancel} %for \cancel
\usepackage{algorithm} %for algorithm environment
\usepackage{algcompatible}
\usepackage[noend]{algpseudocode}
%\usepackage{changepage}%http://ctan.org/pkg/changepage
\usepackage{graphicx} %for includegraphics
\usepackage{tikz}
\usepackage{lscape} %for landscape orientation
%\usepackage{float} %for figures
\usetikzlibrary{shapes.misc, positioning}
\usetikzlibrary{arrows.meta}
\tikzset{>={Latex[width=2mm,length=2mm]}}
\usepackage{caption}

%% \hypersetup{
%%     colorlinks=true,
%%     linkcolor=blue,
%%     filecolor=magenta,
%%     urlcolor=red,
%%     citecolor=teal
%% }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \vspace{-0.1in}
 \section{WEST Code Specifications} \label{specs}
  \vspace{-0.1in}
The code for the WEST program can be found on its %\href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git} KYR: blind review
{GitHub} repository. The MLTL syntax for our program is given as the context free grammar below. In the alphabet, $T$ and $!$ refer to the propositional constants `true' and `false', respectively. $\&$, $v$, $=$, $>$ refer to propositional logic operators `and', `or, `equivalent', and `implies', respectively. Note that the last comma listed is not a typo and indeed part of the alphabet. \\
\textbf{Alphabet}: 
\begin{align*}
    \Sigma = \{&\text{`0' , `1' , `2' , `3' , `4' , `5' , `6' , `7' , `8' , `9' , `T' , `!' , `p' , `$\scriptstyle{\sim}$' , `v' , `\&' , `=' , `\mbox{$>$}' ,}\\
    &\text{ `F' , `G' , `U', `R' , `(' , `)' , `[' , `]' , `:' , `,'}\}
\end{align*}

@@

Let M be a $n+1$ by $n$ matrix, where each of the $n+1$ rows represents a regular expression of length n with commas stripped. If each column has one `$1$', one `$0$', and $n-1$ `$S$'s, then the union of this set of regular expressions can be simplified to $S^n$, the arbitrary computation of length $n$.

@@

@@

    \begin{pmatrix} \label{example1}

@@

\noindent See Appendix \ref{simp appendix} for the proof of the theorem.\\

@@

@@

@@

>>>>

%KYR: need to ensure included packages don't interfere with LNCS style
%\usepackage[utf8]{inputenc}
%\usepackage{amsthm, amsmath, amssymb}
\usepackage{amsfonts} %mathbb
\usepackage{amsmath} %hdots
\usepackage{amssymb} %blacksquare
\usepackage{mathabx} %vDash
\usepackage{mathrsfs} %mathscr
\usepackage{blkarray} %for blockarray
%\usepackage{textcomp}
%\usepackage{xcolor}
%\usepackage{soul}
%\usepackage{ dsfont }
\usepackage{hyperref}
\usepackage{cancel} %for \cancel
\usepackage{algorithm} %for algorithm environment
\usepackage{algcompatible}
\usepackage[noend]{algpseudocode}
%\usepackage{changepage}%http://ctan.org/pkg/changepage
\usepackage{graphicx} %for includegraphics
\usepackage{tikz}
\usepackage{lscape} %for landscape orientation
%\usepackage{float} %for figures
\usetikzlibrary{shapes.misc, positioning}
\usetikzlibrary{arrows.meta}
\tikzset{>={Latex[width=2mm,length=2mm]}}
\usepackage{caption}
\usepackage{mwe}
%% \hypersetup{
%%     colorlinks=true,
%%     linkcolor=blue,
%%     filecolor=magenta,
%%     urlcolor=red,
%%     citecolor=teal
%% }

@@

\section{WEST Algorithm and Analysis} \label{WESTalg}
We now present the  full WEST algorithm, which takes MLTL formula $\phi$ (in NNF) and number of propositional variables $n$, and recursively computes all satisfying temporal regular expressions to $\phi$. We use C++ vectors of strings to represent alternation of regular expressions; for instance $\{t_1, t_2, ..., t_n\} = \bigcup_{i=1}^n t_i$.

    \begin{algorithm}[H]
    \caption{WEST Algorithm}
\begin{algorithmic}[1]
    \Procedure{reg}{string $\phi$, int $n$}
        \If{$\alpha$ is $\top$ or $\bot$}
            \State return reg\_prop\_const($\alpha$, n)
        \EndIf

        \If{$\alpha$ is $p_k$ or $\neg p_k$}
            \State return reg\_prop\_var($\alpha$, n)
        \EndIf

        \If{$\alpha  = \alpha_1 \land \alpha_2$}
            \State return set\_intersect(reg($\alpha_1$), reg($\alpha_2$), n)
        \EndIf

        \If{$\alpha  = \alpha_1 \lor \alpha_2$}
            \State return join(reg($\alpha_1$), reg($\alpha_2$), n)
        \EndIf

        \If{$\alpha = \mathcal{F}_{[a, b]}\alpha_1$}
            \State return reg\_F(reg($\alpha_1$), a, b, n)
        \EndIf

        \If{$\alpha = \mathcal{G}_{[a, b]}\alpha_1$}
            \State return reg\_G(reg($\alpha_1$), a, b, n)
        \EndIf

        \If{$\alpha = \alpha_1 \mathcal{U}_{[a, b]} \alpha_2$}
            \State return reg\_U(reg($\alpha_1$), reg($alpha_2$), a, b, n)
        \EndIf

        \If{$\alpha = \alpha_1 \mathcal{R}_{[a, b]} \alpha_2$}
            \State return reg\_R(reg($\alpha_1$), reg($\alpha_2$), a, b, n)
        \EndIf
    \EndProcedure
\end{algorithmic}
\end{algorithm}

 \vspace{-0.1in}
 \section{WEST Code Specifications} \label{specs}
  \vspace{-0.1in}
The code for the WEST program can be found on its %\href{https://github.com/zwang271/2022-Iowa-State-REU-Temporal-Logic-.git} KYR: blind review
{GitHub} repository. The MLTL syntax for our program is given as the context free grammar below. In the alphabet, $T$ and $!$ refer to the propositional constants `true' and `false', respectively. $\&$, $v$, $=$, $>$ refer to propositional logic operators `and', `or, `equivalent', and `implies', respectively. Note that the last comma listed is not a typo and indeed part of the alphabet. \\
\textbf{Alphabet}: 
\begin{align*}
    \Sigma = \{&\text{`0' , `1' , `2' , `3' , `4' , `5' , `6' , `7' , `8' , `9' , `T' , `!' , `p' , `$\scriptstyle{\sim}$' , `v' , `\&' , `=' , `\mbox{$>$}' ,}\\
    &\text{ `F' , `G' , `U', `R' , `(' , `)' , `[' , `]' , `:' , `,'}\}
\end{align*}

@@

Let M be a $n+1$ by $n$ matrix, where each of the $n+1$ rows represents a regular expression of length n with commas stripped. If each column has one `$1$', one `$0$', and $n-1$ `$S$'s, then the union of this set of regular expressions can be simplified to $S^n$, the arbitrary computation of length $n$. \footnote{See Appendix \ref{simp appendix} for the proof of the theorem.}

@@

\begin{figure}[h!]
\begin{minipage}{.50\textwidth}

@@

    \begin{equation*}
        \begin{pmatrix} \label{example1_regex_simp_thm}

@@

    \end{equation*}
    % \noindent See Appendix \ref{simp appendix} for the proof of the theorem.\\
    \end{minipage}
    \begin{minipage}{.50\textwidth}

@@

    \end{minipage}

@@

% \begin{wrapfigure}{l}{0.5\textwidth} \vspace{-\baselineskip}

@@

% \end{wrapfigure}
